Topic and tone of political news articles in German online media.

### 2018-03-29 paper/docs/04_Modelresults_50.Rmd
add more description

```{r include=FALSE}
library(ggplot2)     # Static data visualization
library(dplyr)       # Data manipulation
library(stringr)     # String manipulation
library(lubridate)   # Date and time manipulation
library(purrr)       # Functional programming
library(tidyr)       # Reshaping
library(magrittr)    # Advanced piping
library(pushoverr)   # Pushover notifications
library(readr)       # Importing data
library(data.table)
library(stm)
library(readxl)
library(Matrix)

@@

@@

>>>>

```{r include=FALSE}
library(ggplot2)     # Static data visualization
library(dplyr)       # Data manipulation
library(stringr)     # String manipulation
library(lubridate)   # Date and time manipulation
library(purrr)       # Functional programming
library(tidyr)       # Reshaping
library(magrittr)    # Advanced piping
library(pushoverr)   # Pushover notifications
library(readr)       # Importing data
library(data.table)
library(stm)
library(readxl)
library(Matrix)
library(psych)
library(xtable)
library(quanteda)

@@

# Data Exploratory Analysis

@@

## Word Count

```{r}
output <- describeBy(btw$text_length, btw$site, mat=T)%>%
  select(group1, n, mean, sd, median, min, max, se)
rownames(output) <- c()

print(xtable(output, type="latex"), file="../writing/tables/wordcount.tex" )

describeBy(btw$text_length, btw$site)
```

```{r}
btw$text_length.cut <- cut(btw$text_length, c(seq(0,2000,1), Inf))
btw <- btw %>% group_by(site) %>%
  mutate(text_length.mean = mean(text_length)) %>%
  ungroup()

ggsave(plot = {
  btw %>%
    ggplot(aes(as.numeric(text_length.cut),
                       group = site)) +
    geom_histogram(aes(y=..density..), alpha=.8, fill = col[3]) + 
    scale_x_continuous(labels = c(seq(0,1500,500), ">2000")) +
    facet_wrap(~site, ncol = 4) +
    labs(x = "Word count", color = "") +
    theme(axis.title = element_text(size = 8),
          axis.text = element_text(size = 6))

}, filename = "../figs/wordcount.png", width = 8, height = 4)
```

![Word Count](../figs/wordcount.png)

## Wordclouds

To summarise the content of the texts, wordclouds help to get a first impression, as they represent the number of words in a corpus. Intuitively the term frequency (tf) of a word is a measure of how important that word may be. The following word cloud is derived from the whole corpus. As can be seen, problems arise with high frequency words. For example "die", "der", and "in" are extremly common but unrelated to the quantity of interest. These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.  We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting. We also remove punctuation character (e.g. ., ,, !, ?, etc.) and all numbers from our corpus.

### Unprocessed Text
```{r message=FALSE, warning=FALSE}
all.corpus <- corpus(btw$text)
df.corpus <- dfm(all.corpus, removePunct = TRUE, removeSymbols = T)
```

```{r message=FALSE, warning=FALSE}
png("../figs/wordcloud.png")
textplot_wordcloud(df.corpus, max.word=300)
dev.off()
```
![Wordcloud 1](../figs/wordcloud.png)

### Processed Text

After completing this steps we were left with 68.576 unique terms in our vocabulary. The following wordclouds is derived from the corpus for each news provider. It becomes evident that these are texts discussing domestic policy issues. The SPD in particular seems to be higly frequent. However, at first glance, there are no obvious differences between the corpus of the different news provider.

```{r eval=FALSE, include=FALSE}
wordclouds <- function(select_site) {
  corp <- btw %>% filter(site %in% select_site)
  corp <- corpus(corp$text_cleaned1)
  corp <- dfm(corp)

  textplot_wordcloud(corp, max.word=200)
}
```

```{r eval=FALSE, include=FALSE}
for (i in unique(btw$site)) {
  png(paste0("../figs/wordcloud_",i,".png"))
  wordclouds(i)
  dev.off()
}
```

<img src="../figs/wordcloud_Bild.de.png", width = "49%" title="Bild.de">
<img src="../figs/wordcloud_DIE WELT.png", width = "49%" title="DIE WELT">
<img src="../figs/wordcloud_FOCUS ONLINE.png", width = "49%" title="FOCUS ONLINE">
<img src="../figs/wordcloud_SPIEGEL ONLINE.png", width = "49%" title="SPIEGEL ONLINE">
<img src="../figs/wordcloud_stern.de.png", width = "49%" title="Stern.de">
<img src="../figs/wordcloud_Tagesschau.de.png", width = "49%" title="Tagesschau.de">
<img src="../figs/wordcloud_ZEIT ONLINE.png", width = "49%" title="ZEIT ONLINE">

### 2018-03-29 paper/writing/doc_backup.tex
add more description

>>>>

% ----------------------
% the online news market
% ----------------------
\section{The online news market}\label{ch_onlinenews}
% Kapitel raus? Bzw. mit Kapitel 4 zusammenlegen.

The market for media content in Germany is characterized by the coexistence of public and private broadcasters. By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change. Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector. In 2017, 22 own websites and 100 apps were operated by public broadcasters on which they offer their content. As a result, public broadcasting no longer only competes with private television and radio stations, but also enters the market for online news. In the following, the characteristics of the market for online news in Germany are briefly described.

Private media outlets naturally appear as two-sided platforms, that allow interaction between two categories of consumers: audiences and advertisers. As the demand on both consumer-sides are linked via indirect network externalities, the market in which media outlets operate are referred to as two-sided or multi-sided markets. The theoretical literature on two-sided markets originates from the analysis of credit card markets \citep{rochet_platform_2003} and was later transferred to the concept of other industries, such as dating agencies, real estate agents, and internet “business-to-business” websites \citep{caillaud_chicken_2003}. The basic concept of two-sided markets was already discussed decades ago in several economic studies, especially on media markets \citep{corden_maximisation_1952}, \citep{gustafsson_circulation_1978}, \citep{blair_pricing_1993}. However, comprehensive analyses have only been carried out in the last ten years, starting with the works of \citet{rochet_platform_2003}, \citet{evans_empirical_2003} and \citet{armstrong_competition_2006}.

Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers. The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention \citep{evans_industrial_2005}. The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM). Advertising can also have an effect on the recipients, which can be either negative or positive, depending on the quality of the advertising. Based on the strength of the indirect network effects, private publishers maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}. Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers. Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall. However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content behind the paywall is very exclusive. As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus, exploit the indirect network effects on the advertising site. In fact, most advertising-financed online magazines earn a large part of their gross margin from advertising \citep{evans_industrial_2005}. In order to maximize their profits, these companies have an interest in attracting as many readers as possible. In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site.

The two-sided market structure of the private news market results in news platforms striving to choose their content in such a way that its reach is as large as possible in order to maximize profits from advertising revenues. \citet{steiner_program_1952} concluded, that profit-maximizing media owners may choose to offer the same content, i.e. content aligned with the tastes of the majority. \citet{gabszewicz_press_2001} study the problem of diversity of the political content of newspapers. They find that the maximum differentiation only prevails if the readers sufficiently value the political differentiation between the newspapers the advertising market is small enough. On the other hand, advertising may also have a positive impact on the media, as it enables publishers to report independently of political parties. \citet{ellman_what_2009} analyze a theoretical framework of a two-sided market for newspaper, where readers value accuracy and advertisers value advert-receptive readers. They found that advertising increases the intensity of competition for readers and therefore raises accuracy of media coverage. However, in the monopolistic case, newspapers under-report news that sufficiently reduces advertiser profits.

Given the crucial role of the media in shaping opinion and promoting democracy, pluralism of opinion and accuracy of information is a major concern of public authorities. Public broadcasting in Germany originated in the post-war period and has always had the task of providing the entire population with independent media. This media offer is intended to guarantee diversity of opinion within the media landscape and to be economically and politically independent. The former is given by the fact that the public media are financed by compulsory fees. To take into account the distinct nature of digital media, the Interstate Broadcasting Agreement (Rundfunkstaatsvertrag) also regulates the scope for action of online services offered by public service broadcasting since 2007. Accordingly, public media are not allowed to distribute purchased content and must - depending on the category of content - set a time limit on its accessibility. In addition, there is a strict advertising ban and prohibition of regional reporting.

The market for media content in Germany is characterized by the coexistence of public and private broadcasters. By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change. Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector. As a result, public broadcasting no longer only competes with private television and radio stations, but also enters the market for online news.
